### 2022-11-28 chien_sim.Rmd
update

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r cars}
covid <- read_csv("owid-covid-data.csv")
```

```{r}
china <- covid %>% 
  filter(location=="China") %>% 
  filter(date <= "2020-03-28") %>% 
  filter(date >= "2020-01-22") %>% 
  select(date, total_cases, total_deaths) %>% 
  mutate(days = c(1:67))
```

```{r}
ggplot() +
  geom_point(aes(x = date, y = total_cases), data = china)
#+ geom_smooth(aes(x = date, y = total_cases), data=italy)
ggplot() +
  geom_point(aes(x = date, y = total_deaths), data = china)
#+ geom_smooth(aes(x = date, y = total_deaths), data=italy)
```

```{r}
x <- 1:67
ggplot(china,aes(x)) +
  geom_point(aes(x = days, y = total_cases)) +
  stat_function(fun=function(x) 40000 + 40000 * erf(0.11*x - 2))

ggplot(china,aes(x)) +
  geom_point(aes(x = days, y = total_deaths)) +
  stat_function(fun=function(x) 1600 + 1600 * erf(0.071*x - 1.8))
```

```{r}
italy <- covid %>% 
  filter(location=="Italy") %>% 
  filter(date <= "2020-04-21") %>%
  filter(date >= "2020-02-15") %>%
  select(date, total_cases, total_deaths) %>% 
  mutate(days = c(1:67))
italy[45:67,] <- NA
```

```{r}
ggplot() +
  geom_point(aes(x = date, y = total_cases), data = italy)
#+ geom_smooth(aes(x = date, y = total_cases), data=italy)
ggplot() +
  geom_point(aes(x = date, y = total_deaths), data = italy)
#+ geom_smooth(aes(x = date, y = total_deaths), data=italy)
```

```{r}
x <- 1:67
ggplot(italy,aes(x)) +
  geom_point(aes(x = days, y = total_cases)) +
  stat_function(fun=function(x) 100000 + 100000 * erf(0.07*x - 3))

ggplot(italy,aes(x)) +
  geom_point(aes(x = days, y = total_deaths)) +
  stat_function(fun=function(x) 11000 + 11000 * erf(0.068*x - 3))
```
